Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-12-08 article.tex
Jane approved

Compilation refers to the process of translating from one language to another, most often from a high-level programming language intended for humans to work with, to machine- or bytecode intended to be executed on a target platform. This process can be divided into several distinct phases, which are grouped into one of two stages colloquially referred to as the \textit{frontend} and \textit{backend}. The former translating a high-level programming language to an \textit{intermediate representation} (IR) and the latter translating IR to executable machine code of a target architecture or bytecode of a target \textit{virtual machine} (VM).

@@

Continuous sequences of instructions are referred to as \textit{basic blocks}. A basic block is defined as a sequence of instructions with no branches in or out except for the first instruction, which follows immediately either the function entry point or a label,  and the last instruction, which either terminates or transfers the flow of execution, hence these are often referred to as terminators and can be thought of as a different categoriy of instructions entirely.

@@

\newpage
\subsection{Benchmarking}

>>>>

Compilation refers to the process of translating from one language to another, most often from a high-level programming language intended for humans to work with, to machine- or bytecode intended to be executed on a target architecture. This process can be divided into several distinct phases, which are grouped into one of two stages colloquially referred to as the \textit{frontend} and \textit{backend}, the former translating a high-level programming language to an \textit{intermediate representation} (IR) and the latter translating IR to executable machine code of a target architecture or bytecode of a target \textit{virtual machine} (VM).

@@

A continuous sequence of instructions is referred to as a \textit{basic block}, which is defined as a sequence with no branches in or out except for the first instruction, following immediately after the function entry or a label, and the last instruction, either terminates or transferring the flow of execution. These are often referred to as terminators and can be thought of as an entirely different categoriy of instructions. % TODO: måske drop 'can be thought of'

@@

\subsection{Benchmarking}
